%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    {\Huge \scshape Samuel Lloyd-Lindholm} \\ \vspace{1pt}
    Surrey, United Kingdom \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ +44 (0)737 9985 422 ~ \href{mailto:sam@lllind.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{sam@lllind.com}} ~ 
    \href{http://www.linkedin.com/in/samlllind}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/samlllind}}  ~
    \href{https://github.com/NaNuNaNu}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/NaNuNaNu}}
    \vspace{-8pt}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
  \resumeSubheading
      {Portsmouth University}{2021 -- Current}
      {PhD Mathematics}{Portsmouth, UK}
    \resumeSubheading
      {MITx (Remote)}{2019}
      {Data Analysis in Social Science (Certificate)}{Remote}
    \resumeSubheading
      {Imperial College (Remote)}{2018}
      {Mathematics for Machine Learning (Certificate)}{Remote}
    \resumeSubheading
      {Cranfield University}{2006 -- 2007}
      {MSc Astronautics and Space Engineering (No award)}{Cranfield, UK}
    \resumeSubheading
      {Queen Mary, University of London}{2002 -- 2005}
      {BSc Theoretical Physics (2.1)}{London, UK}
    
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
  
  \resumeSubheading
      {Lloyd-Lindholm Ltd}{2021 -- Current}
      {Director}{London, UK}
      \resumeItemListStart
        \resumeItem{Independent consulting on software engineering and mathematical methods for trading systems.}
        \resumeItem{General software development, Go-lang, Python, back-end platforms, low-latency and high frequency systems.}
        \resumeItem{Trading strategy development and analysis.}
      \resumeItemListEnd

    \resumeSubheading
      {Syndicate}{2014 -- Current}
      {Founding Member \& Partner}{London, UK}
      \resumeItemListStart
        \resumeItem{Leading platform development \& design process of a distributed low latency platform for automated trading.}
        \resumeItem{Software development of key systems including machine learning system integration, protocol design, low latency \& highly parallel systems and critical trading services. Documentation and maintenance of our software stack.}
        \resumeItem{Strategic business management including administrative, financial, legal and cross-jurisdictional matters.}
        \resumeItem{Mentoring of junior team members.}
      \resumeItemListEnd

    \resumeSubheading
      {OpenXO}{2013 -- 2014}
      {Platform Lead \& Employee Nr.1}{London, UK}
      \resumeItemListStart
        \resumeItem{In charge of platform development.}
        \resumeItem{Design, architecture and hands on work building the core platform.}
    \resumeItemListEnd
    
    \resumeSubheading
      {Betfair}{2010 -- 2013}
      {Platform Engineer}{London, UK}
      \resumeItemListStart
        \resumeItem{Part of the core exchange engineering team tasked with developing and maintaining the betting exchange platform.}
        \resumeItem{Responsible for supporting business critical components also during out of hours.}
    \resumeItemListEnd
    
    \resumeSubheading
      {ITT-Visual Information Solutions}{2007 -- 2010}
      {Consultant \& Developer}{Bracknell, UK}
      \resumeItemListStart
        \resumeItem{Consulting and developing custom solutions in image processing for defence, scientific, environmental and medical applications.}
        \resumeItem{Sales work as part of consultancy process.}
        \resumeItem{Presenting seminars on technical topics and running workshops on programming techniques.}
    \resumeItemListEnd
    
  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
    
        \resumeProjectHeading
              {\textbf{Order book trading system} $|$ \emph{Golang, Python}}{2021}
              \resumeItemListStart
                \resumeItem{Golang based trading gateway platform for interacting with trading venues.}
                \resumeItem{Analysis of order book level data.}
                \resumeItem{Foundational algorithmic design based on category theory and lattice theory.}
              \resumeItemListEnd
              \vspace{-13pt}
    
        \resumeProjectHeading
          {\textbf{Esports market making bot} $|$ \emph{Golang, Python, SQL, NodeJS, AWS}}{2021}
          \resumeItemListStart
            \resumeItem{Web scraping and API integration to collect live data of esports events and market prices.}
            \resumeItem{Research into automated market making.}
            \resumeItem{Central event storage system in PostgresQL.}
            \resumeItem{System deployment on AWS including DB, service nodes, front end console and downtime warning elements.}
            \resumeItem{Basic market making strategy analysis using Python.}
            \resumeItem{Golang core service elements tasked with making real money trading decisions.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{Crypto currency feed} $|$ \emph{Golang, NodeJS, SQL, HTML, AWS}}{2019}
          \resumeItemListStart
            \resumeItem{Created a Crypto feed aggregator that consumed many sources of Crypto price \& trade volume data.}
            \resumeItem{Data was stored in a PostgresQL database and queryable through he platform via exposed API calls.}
            \resumeItem{Basic Python analysis of the price/vol data.}
          \resumeItemListEnd 
          \vspace{-13pt}
          \resumeProjectHeading
          {\textbf{Event Mapping system} $|$ \emph{Golang, VueJs, SQL, AWS}}{2015}
          \resumeItemListStart
            \resumeItem{Mapping of sports events from disparate sources into an internal representation.}
            \resumeItem{Storage in PostgresQL database.}
            \resumeItem{Front end work for interacting with the data.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd
\vspace{-15pt}


%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Golang, Python, Java, SQL, JS} \\
     \textbf{Technologies/Frameworks}{: Unix, AWS, Git/hub, VIM, LaTeX} \\
     \textbf{General}{: Research, Documentation, Mathematics, Software Architecture \& Design} \\
    }}
 \end{itemize}
 \vspace{-16pt}

\end{document}